---
title: "spmle"
author: "Philipp Hunziker"
date: "November 25, 2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# System Requirements

Python 2.7 (tested) or Python 3.6 (not tested). Also, [conda](https://conda.io/docs/user-guide/install/windows.html) if on Windows.

# Installation

Install `spmle` directly from this repository:

```{r install, eval=FALSE}
devtools::install_github("hunzikp/spmle")
```

In case you don't have scipy and numpy installed (or don't know what these are), run the following in an R console:
```{r dependencies, eval=FALSE}
spmle::install_pydep()
```
The command installs the Python dependencies in the `r-reticulate` virtual environment.

# Usage

To use the package you need to specify a python binary or virtual environment where scipy and numpy are installed. If use used the `install_pydep()` command from above:  

```{r usage, eval=FALSE}
library(reticulate)
library(spmle)
reticulate::use_virtualenv("r-reticulate")  # In Unix
reticulate::use_condaenv("r-reticulate")  # In Windows
```

# Examples

See [here](scripts/mbdm_testing.md).
