---
title: "spmle"
author: "Philipp Hunziker"
date: "June 21, 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# System Requirements

To use the (optional but recommended) Python speed-up, you need Python 3.6+ (and [conda](https://conda.io/docs/user-guide/install/windows.html) if on Windows).


# Installation

Install `spmle` directly from this repository:

```{r install, eval=FALSE}
devtools::install_github("hunzikp/spmle")
```

In case you don't have scipy and numpy installed (or don't know what these are) and you want to use the Python speed-up, run the following in an R console:
```{r dependencies, eval=FALSE}
spmle::install_pydep()
```
This command installs the Python dependencies in the `r-reticulate` virtual environment.

# Usage

To use the Python speed-up you need to specify a python binary or virtual environment where scipy and numpy are installed. If you ran the `install_pydep()` command above, then you can use the following:  

```{r usage, eval=FALSE}
library(reticulate)
library(spmle)
reticulate::use_virtualenv("r-reticulate")  # In Unix
reticulate::use_condaenv("r-reticulate")  # In Windows
```

# Examples

See [here](scripts/stmodel_testing.md).
